CLT Results

### 2022-05-18 analysis/clt_irt_analysis.Rmd
add model comparison

```{r}
loo_compare(irt1, irt2, irt3)%>%as_tibble(rownames = "model")
```

@@

```{r}
loo_compare(irt3, irt3_dif_sex)%>%as_tibble(rownames = "model")
```

@@

```{r}
loo_compare(irt3, irt3_dif_order)%>%as_tibble(rownames = "model")
```

>>>>

```{r}
mc1 <- loo_compare(irt1, irt2, irt3)%>%as_tibble(rownames = "model")

write_csv(mc1, "../saves/model_comparison.csv")
```

@@

```{r}
mc2 <- loo_compare(irt3, irt3_dif_sex)%>%as_tibble(rownames = "model")

write_csv(mc2, "../saves/model_comparison_dif_sex.csv")
```

@@

```{r}
mc3 <- loo_compare(irt3, irt3_dif_order)%>%as_tibble(rownames = "model")

write_csv(mc3, "../saves/model_comparison_dif_order.csv")
```
